\documentclass{article}
\begin{document}
John F. Lake, Jr. HW 8

\begin{enumerate}
\item Objects in perl are references associated with classes (blueprints).  Objects in perl, like other languages, have methods and data members.  The bless function in perl is used by saying "bless REF, CLASSNAME".  This tells the object REF that it is now an object in the CLASSNAME package. 
\item A hash is a data structure with key-value pairs.  An array is simply a list of objects.  They are similar because they contain multiple objects, but a hash contains key-value pairs for everything (such as a word in a dictionary having a definition).  
\item Packages in Perl is code in a specific namespace - they are used to avoid variable name issues.  The scope of variables in packages is within the namespace of that package.  When you use the "my" keyword in perl you are specifying the scope of the succeeding variable to be in the enclosed block.  
\item The default variable, \$\_, is used as the default argument for many functions, and is the variable used in every iteration of a foreach loop if you do not specify the variable name.  The default array, @\_, is a variable which holds every parameter to a given function.  These are used to save time, but they can make code difficult to read.   
\item Perl is different from other scripting languages because it has a rich variety of syntax, has the capability of a compiled programming language, and has the functionality of a scripting language. It is easy to use, fast, and powerful.  
\end{enumerate}


\end{document}
